In the course of this project we tried to predict House Prices using a number of different regression and machine learning algorithms. The aim of this procedure was mostly to evaluate the different algorithms against each other rather than optimizing the predictions of one single model. As a data source we chose the data from a Kaggle Competition that is currently running. This data contains final sale prices of houses in the city of Ames, Iowa from the Year 2010 as well as a large number of different explanatory variables for each property. On a training subset of this data we trained different types of regression models as well as a random forest and a gradient boosting machine. While we used the statistical programming language \textit{R} for the entire project we used implementations of these models from different packages and even implemented some modelling aspects ourselves. The structure of this paper will be the following: First we will give a theoretical overview over each of the models that we used explaining the main ideas and mathematical theory behind them. Afterwards we will demonstrate and illustrate how we used \textit{R} to implement, train and tune these models. In the third section we will illustrate our evaluation scenario doing some explorative analysis on the housing data and describing how we preprocessed the data and evaluated the models. After having presented the results for each model we complete the study by summarising our findings and conclusions. 